method

### 2021-11-19 06_Paper/ER-ED/method.Rmd
added paragraph to statistics

[...]

>>>>

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
The level of significance was set to $alpha$ = .05.
To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted.
